### 2025-04-09 mixed-models.qmd
20250408 - plotly

ggplotly(
  plot_scatterplotFantasyPointsByAgeQB,
  tooltip = c("age","fantasyPoints","text","label"))
```

@@

ggplotly(
  plot_scatterplotFantasyPointsByAgeFB,
  tooltip = c("age","fantasyPoints","text","label"))
```

@@

ggplotly(
  plot_scatterplotFantasyPointsByAgeRB,
  tooltip = c("age","fantasyPoints","text","label"))
```

@@

ggplotly(
  plot_scatterplotFantasyPointsByAgeWR,
  tooltip = c("age","fantasyPoints","text","label"))
```

@@

ggplotly(
  plot_scatterplotFantasyPointsByAgeTE,
  tooltip = c("age","fantasyPoints","text","label"))
```

@@

ggplotly(
  plot_rawFantasyPointsByAgeQB,
  tooltip = c("age","fantasyPoints","text","label"))
```

@@

ggplotly(
  plot_rawFantasyPointsByAgeFB,
  tooltip = c("age","fantasyPoints","text","label"))
```

@@

ggplotly(
  plot_rawFantasyPointsByAgeRB,
  tooltip = c("age","fantasyPoints","text","label"))
```

@@

ggplotly(
  plot_rawFantasyPointsByAgeWR,
  tooltip = c("age","fantasyPoints","text","label"))
```

@@

ggplotly(
  plot_rawFantasyPointsByAgeTE,
  tooltip = c("age","fantasyPoints","text","label"))
```

@@

ggplotly(
  plot_individualFantasyPointsRandomIntercepts,
  tooltip = c("age","fantasyPoints_randomIntercepts","text","label")
)
```

@@

ggplotly(
  plot_individualFantasyPointsPosition,
  tooltip = c("age","fantasyPoints_position","text","label")
)
```

@@

ggplotly(
  plot_individualFantasyPointsFixedLinearSlopes,
  tooltip = c("age","fantasyPoints_fixedLinearSlopes","text","label")
)
```

@@

ggplotly(
  plot_individualFantasyPointsRandomLinearSlopes,
  tooltip = c("age","fantasyPoints_randomLinearSlopes","text","label")
)
```

@@

ggplotly(
  plot_individualFantasyPointsRandomLinearFixedQuadracticSlopes,
  tooltip = c("age","fantasyPoints_randomLinearFixedQuadraticSlopes","text","label")
)
```

@@

ggplotly(
  plot_individualFantasyPointsRandomLinearFixedQuadraticSlopesInteraction,
  tooltip = c("age","fantasyPoints_randomLinearFixedQuadraticSlopesInteraction","text","label")
)
```

@@

ggplotly(
  plot_individualFantasyPointsByAgeQB,
  tooltip = c("age","fantasyPoints_gam","text","label")
)
```

@@

ggplotly(
  plot_individualFantasyPointsByAgeFB,
  tooltip = c("age","fantasyPoints_gam","text","label")
)
```

@@

ggplotly(
  plot_individualFantasyPointsByAgeRB,
  tooltip = c("age","fantasyPoints_gam","text","label")
)
```

@@

ggplotly(
  plot_individualFantasyPointsByAgeWR,
  tooltip = c("age","fantasyPoints_gam","text","label")
)
```

@@

ggplotly(
  plot_individualFantasyPointsByAgeTE,
  tooltip = c("age","fantasyPoints_gam","text","label")
)
```

>>>>

plotly::ggplotly(
  plot_scatterplotFantasyPointsByAgeQB,
  tooltip = c("age","fantasyPoints","text","label"))
```

@@

plotly::ggplotly(
  plot_scatterplotFantasyPointsByAgeFB,
  tooltip = c("age","fantasyPoints","text","label"))
```

@@

plotly::ggplotly(
  plot_scatterplotFantasyPointsByAgeRB,
  tooltip = c("age","fantasyPoints","text","label"))
```

@@

plotly::ggplotly(
  plot_scatterplotFantasyPointsByAgeWR,
  tooltip = c("age","fantasyPoints","text","label"))
```

@@

plotly::ggplotly(
  plot_scatterplotFantasyPointsByAgeTE,
  tooltip = c("age","fantasyPoints","text","label"))
```

@@

plotly::ggplotly(
  plot_rawFantasyPointsByAgeQB,
  tooltip = c("age","fantasyPoints","text","label"))
```

@@

plotly::ggplotly(
  plot_rawFantasyPointsByAgeFB,
  tooltip = c("age","fantasyPoints","text","label"))
```

@@

plotly::ggplotly(
  plot_rawFantasyPointsByAgeRB,
  tooltip = c("age","fantasyPoints","text","label"))
```

@@

plotly::ggplotly(
  plot_rawFantasyPointsByAgeWR,
  tooltip = c("age","fantasyPoints","text","label"))
```

@@

plotly::ggplotly(
  plot_rawFantasyPointsByAgeTE,
  tooltip = c("age","fantasyPoints","text","label"))
```

@@

plotly::ggplotly(
  plot_individualFantasyPointsRandomIntercepts,
  tooltip = c("age","fantasyPoints_randomIntercepts","text","label")
)
```

@@

plotly::ggplotly(
  plot_individualFantasyPointsPosition,
  tooltip = c("age","fantasyPoints_position","text","label")
)
```

@@

plotly::ggplotly(
  plot_individualFantasyPointsFixedLinearSlopes,
  tooltip = c("age","fantasyPoints_fixedLinearSlopes","text","label")
)
```

@@

plotly::ggplotly(
  plot_individualFantasyPointsRandomLinearSlopes,
  tooltip = c("age","fantasyPoints_randomLinearSlopes","text","label")
)
```

@@

plotly::ggplotly(
  plot_individualFantasyPointsRandomLinearFixedQuadracticSlopes,
  tooltip = c("age","fantasyPoints_randomLinearFixedQuadraticSlopes","text","label")
)
```

@@

plotly::ggplotly(
  plot_individualFantasyPointsRandomLinearFixedQuadraticSlopesInteraction,
  tooltip = c("age","fantasyPoints_randomLinearFixedQuadraticSlopesInteraction","text","label")
)
```

@@

plotly::ggplotly(
  plot_individualFantasyPointsByAgeQB,
  tooltip = c("age","fantasyPoints_gam","text","label")
)
```

@@

plotly::ggplotly(
  plot_individualFantasyPointsByAgeFB,
  tooltip = c("age","fantasyPoints_gam","text","label")
)
```

@@

plotly::ggplotly(
  plot_individualFantasyPointsByAgeRB,
  tooltip = c("age","fantasyPoints_gam","text","label")
)
```

@@

plotly::ggplotly(
  plot_individualFantasyPointsByAgeWR,
  tooltip = c("age","fantasyPoints_gam","text","label")
)
```

@@

plotly::ggplotly(
  plot_individualFantasyPointsByAgeTE,
  tooltip = c("age","fantasyPoints_gam","text","label")
)
```

### 2025-04-09 time-series-analysis.qmd
20250308 - R packages
20250308 - citations
20250408 - plotly

Adapted from: <https://rc2e.com/timeseriesanalysis> (archived at <https://perma.cc/U5P6-2VWC>).

@@

@@

ggplotly(
  plot_individualFantasyPointsByAgeQB,
  tooltip = c("age","fantasyPoints_bayesian","text","label")
)
```

@@

ggplotly(
  plot_individualFantasyPointsByAgeRB,
  tooltip = c("age","fantasyPoints_bayesian","text","label")
)
```

@@

ggplotly(
  plot_individualFantasyPointsByAgeWR,
  tooltip = c("age","fantasyPoints_bayesian","text","label")
)
```

@@

ggplotly(
  plot_individualFantasyPointsByAgeTE,
  tooltip = c("age","fantasyPoints_bayesian","text","label")
)
```

>>>>

Adapted from: <https://rc2e.com/timeseriesanalysis> [@Long2019; archived at <https://perma.cc/U5P6-2VWC>].

@@

Using the `forecast` package [@R-forecast; @Hyndman2008_packages]:

@@

plotly::ggplotly(
  plot_individualFantasyPointsByAgeQB,
  tooltip = c("age","fantasyPoints_bayesian","text","label")
)
```

@@

plotly::ggplotly(
  plot_individualFantasyPointsByAgeRB,
  tooltip = c("age","fantasyPoints_bayesian","text","label")
)
```

@@

plotly::ggplotly(
  plot_individualFantasyPointsByAgeWR,
  tooltip = c("age","fantasyPoints_bayesian","text","label")
)
```

@@

plotly::ggplotly(
  plot_individualFantasyPointsByAgeTE,
  tooltip = c("age","fantasyPoints_bayesian","text","label")
)
```
